---
title: "agCLIM50"
author: "Michiel van Dijk"
date: "13 September 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_data, echo = FALSE, message = FALSE}
library(readr)
dataPath <- "D:\\Dropbox\\AgClim50 scenario results"
TOTAL <- read.csv(file.path(dataPath, "ModelResults\\TOTAL_2016-09-14.csv"))
```

# Introduction
This document provides notes on the agCLIM50 model results database. At present the database includes data from the following models:

* MAGNET
* GLOBIOM
* MAgPIE
* IMAGE
* CAPRI

The database is stored in the project dropbox model results folder under the name _TOTAL.csv_. In line with the reporting template the database includes the following variables:

- year
- item
- region
- variable
- unit
- value 
- model
- scenario
- index: an index (2010 = 1)

# Missing and 'strange' data
At the moment I am doing some quick checks to analyse if data is missing or otherwise is not correct. The checks involve making graphs of all variables across models and regions, which are stored in the folder _graphs_ and several simple cross tables (see below). I only had time to take a superficial look at the data but found the following:

## GDP, POP and YEXO
These are the three key exogenous drivers and are supposed to be the same (overlapping lines) across models. Nevertheless, the figures show (minor) differences. *POPT* seems consistent but *GDPT* shows large differences for a number of regions. Also yield (only available for MAGNET and GLOBIOM) is not the same.

## MAgPIE
* GDPT and POPT are 0 and, hence, result in infinite numbers when calculating the index. I set them to NA.
* Some other data is already infinite in the raw data file, also set to NA.
* Two items seem to have the wrong name. I recoded _LVS_ into _LSP_ and _SUG_ into _SGC_. Please check.
* For several regions/scenarios _XPRP_ is missing data for the year 2010 and, hence, the index cannot be calculated.
* Several variables, including _XPRP_ are not calculated over _AGR_ and _TOT_.
* MAgPIE includes multiple units for one variable (see below). E.g. 1000 t prt and 1000 t for PROD. I use 1000 t. Please correct. 

## GLOBIOM
* Several variables (see table below) carry two units (often dm and fm), which is not in line with the template. This results in duplicated values in the figures causing problems. Please correct. I decided to use the units: 1000 t and fm t/ha (excluding 1000 dm t and dm t/ha)
* For _IMPO_, _EXPO_ and _NETT_ for some regions, data for 2010 (and other years is missing) and therefore the index cannot be calculated. Also the naming of some other units is not in line with the template (see below). Please correct.

## CAPRI
* CAPRI does not present values for 2010 for each of the scenarios. It does however present a _BASELINE_. I assume the _BASELINE_ values can be used for 2010 for each scenario.
* Even after adding the baseline values, it seems that _EXPO_TOT_ and _OTHU_ for some variables year 2010 is missing. I set those values to NA.
* CAPRI is missing many variables and does not present unit information (see coverage).
* CAPRI includes many more regions. I filter them out. 


# IMAGE
* Does not cover all variables.

# MAGNET
* Does not include information on CALO although the model can generate this. 

\newpage
# GLOBIOM unit coverage
```{r GLOBIOM, echo = FALSE, message = FALSE}
library(dplyr)
GLOBIOM <- read_csv(file.path(dataPath, "ModelResults\\agclim50_GLOBIOM_20160907.csv")) %>%
  rename(model = Model, scenario = Scenario, region = Region, item = Item, unit = Unit, variable = Variable, year = Year, value = Value) %>%
  mutate(variable = toupper(variable))
xtabs(~variable + unit, data = GLOBIOM)
```


\newpage
# MAgPIE unit coverage
```{r MAgPIE, echo = FALSE, message = FALSE}
library(dplyr)
MAgPIE <- read_csv(file.path(dataPath, "ModelResults\\agclim50_MAgPIE.csv")) %>%
  rename(model = Model, scenario = Scenario, region = Region, item = Item, unit = Unit, variable = Variable, year = Year, value = Value)
xtabs(~variable + unit, data = MAgPIE)
```


\newpage
# Variable coverage
```{r variable, echo = FALSE, message = FALSE}
xtabs(~ variable + model, data = TOTAL)
```

\newpage
# Region coverage
```{r region, echo = FALSE, message = FALSE}
xtabs(~ region + model, data = TOTAL)
```

\newpage
# Item coverage
```{r item, echo = FALSE, message = FALSE}
xtabs(~ item + model, data = TOTAL)
```

\newpage
# Unit coverage
```{r unit, echo = FALSE, message = FALSE}
xtabs(~ unit + model, data = TOTAL)
```

\newpage
# Scenario coverage
```{r scenario, echo = FALSE, message = FALSE}
xtabs(~ scenario + model, data = TOTAL)
```
